\documentclass[10pt]{article}
% use pdflatex command and not pdftex
\usepackage[margin=3cm]{geometry}
\usepackage{hyperref}
\usepackage{array, xcolor}
\definecolor{lightgray}{gray}{0.8}
% \usepackage{bibentry}
% \bibliographystyle{plain}
% \nobibliography*
\usepackage{multicol}
\usepackage{enumitem}
\newenvironment{myitemize}
{ \begin{itemize}[topsep=0pt]
  	\vspace{-4pt}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}     }
{ \end{itemize}                  } 
\newenvironment{skillitemize}
{ \begin{itemize}[topsep=0pt,label={}]
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}     }
{ \end{itemize}                  }
\newcommand{\breakrule}{
  	\color{lightgray}
  	\vspace{-4pt}
	\begin{center}
		\noindent\rule{7cm}{0.5pt}
	\end{center}
	}
% title
\title{\bfseries\Huge Justin Milano}
\author{milanojustin@gmail.com}
\date{}

\begin{document}
% title
\begin{center}
	{\bf \Huge Justin Milano}\\
	\vspace{5pt}
	{\bf \large milanojustin@gmail.com}\\
  {\bf \large (801) 560-9587}
\end{center}
%\vspace{5mm}
\vspace{-5pt}
\section*{Professional Experience}

\noindent
{\large {\bf Summary}} \\
IT professional with experience in network design, documentation, and maintenance. Expertise in Linux administration, strong problem solving skills, and the ability to prioritize responsibilities and timelines. Work well in a teaming environment. \\

\noindent
{\large {\bf DevOps Engineer}, Western Governors University\hfill Oct. 2015-Present } \\
{\bf Responsibilities:}
\begin{myitemize}
  \item Administration and maintenance of Attlassian software suite including:
    \begin{itemize}
      \item Jira
      \item Confluence
      \item Bitbucket
      \item Bamboo
      \item Crowd
    \end{itemize}
  \item Managed and maintained various RedHat GNU/Linux nodes.
  \item Chef automation
  \item Participation in on-call rotation
\end{myitemize} 
{\bf Projects:}
\begin{myitemize}
  \item Consolidation of two independent Confluence instances.
  \item Consolidation of two independent Jira instances.
  \item Chef wrapper cookbook for auto-scaling elasticsearch cluster
\end{myitemize} 
{\breakrule}

\noindent
{\large {\bf Infrastructure Engineer}, Discovery Research Group \hfill Aug. 2013-Sep. 2015 } \\
{\bf Responsibilities:}
\begin{myitemize}
  \item Managed and maintained a farm of 20 physical servers in a lights out datacenter.
  \item Managed and maintained VMware ESX cluster hosting 41 virtual machines.
  \item Administration of Debian GNU/Linux systems. (Most of our systems fell into this category.)
  \item Administration of RedHat GNU/Linux systems. (We had a handful of these systems. They were all used to run some version of Asterisk.)
  \item Administration of Windows Server 2008 systems. (We had a handful of these systems. Their purposes included: Domain controllers, file servers, Terminal Services servers, and Veeam backup.)
  \item Administration of Windows 7 workstations for end users.
\end{myitemize} 
{\bf Projects:}
\begin{myitemize}
  \item Implementation of OTRS as a change management database.
  \item Reorganization of all physical components in our rack space at the data center.
  \item Implementation of Ansible for automating administration of our GNU/Linux hosts.
  \item Implementation of quarterly Nessus vulnerability scans.
\end{myitemize} 

{\breakrule}

\noindent
{\large {\bf Linux Administrator}, HostGator\hfill Aug. 2013-Apr. 2014 } \\
{\bf Responsibilities:}
\begin{myitemize}
  \item Tier 1 email support of Apache, Mysql, Bind, cPanel, OpenVZ, WordPress and various other content management systems.
\end{myitemize} 

{\breakrule}

\noindent
{\large {\bf Independent Contractor}, ForeverGreen\hfill Sep. 2011-Apr. 2012 } \\
{\bf Responsibilities:}
\begin{myitemize}
  \item Network analysis and documentation.
  \item End user support.
\end{myitemize} 
{\bf Projects:}
\begin{myitemize}
  \item Documentation of the layout of the network that they inherited from a related company.
\end{myitemize} 

{\breakrule}

\noindent
{\large {\bf Systems Administrator}, Maakoa\hfill Aug. 2010-Apr. 2011 } \\
{\bf Responsibilities:}
\begin{myitemize}
  \item Administration of a handful of servers in a small office environment. (Mostly Windows Server systems for AD, file shares, etc.)
  \item End user Support.
\end{myitemize} 
{\bf Projects:}
\begin{myitemize}
 \item Development of a web application that interacted with a financial institution via their API. This was run on a Windows server but utilized Apache, MySQL, and Perl.
\end{myitemize} 

{\breakrule}

\noindent
{\large {\bf Computer Lab Assistant}, Jordan School District\hfill Sep. 2003-May. 2005 } \\
{\bf Responsibilities:}
\begin{myitemize}
  \item  Instructed and assisted students in the lab.
  \item  Various end user support tasks for teachers and faculty.
\end{myitemize} 

\section*{Skills}

\begin{minipage}[ht]{0.48\textwidth}
	{\bf Server Administration}
	\begin{skillitemize}
		\item GNU/Linux (RedHat, Debian, BSD)
		\item Windows Server
		\item VMware ESX
		\item Asterisk
		\item Apache
		\item Nginx
		\item MySQL
	\end{skillitemize}
\end{minipage}
\begin{minipage}[ht]{0.48\textwidth}
	{\bf Scripting/Automation}
	\begin{skillitemize}
		\item Bash
		\item Python
		\item Perl
		\item Ansible
    \item Chef
    \item 
    \item 
	\end{skillitemize}
\end{minipage}

\vspace{8pt}
\noindent
\begin{minipage}[ht]{0.48\textwidth}
	{\bf Network Administration}
	\begin{skillitemize}
		\item iptables
		\item Bind (DNS)
		\item PF(Open BSD's Packet Filter)
		\item Nessus
	\end{skillitemize}
\end{minipage}

\section*{Education/Certifications}
\begin{myitemize}
	\item Bachelor of Science in Computer Science, Weber State University (2010)
  \item Tenable Certified Nessus Auditor. (Received 5/14)
\end{myitemize}
\section*{References}
\begin{myitemize}
  \item Chris Sohns (Discovery Research Group) - (970) 980-4380
  \item Josh Staley (Western Governors University) - (801) 699-3440
  \item Mark Kimmig (Personal) - (801) 599-0800
\end{myitemize}
\end{document}
